RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-10-10 doc/paper.tex
Some results are in tex.

@@

 \\

>>>>

\begin{table}[!htb]
	\caption{Comparison without noise}\label{tab:comp_noise0}
	\centering
		\begin{tabular}{l|rrr|rrr} \hline
			& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
			Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
			RILS-ROLS&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
			AIFeynman&55.78&27.14&52.69&78.51&35.71&73.9\\
			GP-GOMEA&26.83&29.46&27.12&71.55&71.43&71.54\\
			AFP\_FE&26.98&20&26.23&59.05&28.57&55.77\\
			ITEA&22.41&7.14&20.77&27.59&21.43&26.93\\
			AFP&21.12&15.18&20.48&44.83&25&42.69\\
			DSR&19.72&19.64&19.71&25&14.29&23.85\\
			Operon&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
			gplearn&16.27&8.93&15.48&32.76&7.14&30\\
			SBP-GP&12.72&11.61&12.6&73.71&78.57&74.23\\
			EPLEX&12.39&8.93&12.02&46.98&21.43&44.23\\
			BSR&2.48&0.89&2.31&10.78&21.43&11.93\\
			FEAT&0&0.89&0.1&39.66&42.86&40\\
			FFX&0&0&0&0&0&0\\
			MRGP&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
			\hline
		\end{tabular}
\end{table}

\begin{table}[!htb]
	\caption{Comparison with noise level 0.001}\label{tab:comp_noise0001}
	\centering
		\begin{tabular}{l|rrr|rrr} \hline
			& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
			Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
			RILS-ROLS&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
			DSR&16.81&18.75&17.02&26.29&14.29&25\\
			gplearn&15.84&8.93&15.1&24.14&7.14&22.31\\
			AFP\_FE&15.95&6.43&14.92&57.76&28.57&54.62\\
			AFP&14.87&7.14&14.04&44.83&25&42.69\\
			EPLEX&10.02&2.68&9.23&48.71&21.43&45.77\\
			AIFeynman&1.49&13.73&2.81&9.73&35.71&12.53\\
			ITEA&1.94&4.46&2.21&26.72&21.43&26.15\\
			GP-GOMEA&1.62&0.89&1.54&72.84&71.43&72.69\\
			Operon&0.34&0&0.31&\bf{81.9}&\bf{92.86}&\bf{83.08}\\
			FFX&0.11&0&0.1&19.4&14.29&18.85\\
			FEAT&0&0.89&0.1&13.79&50&17.69\\
			SBP-GP&0&0&0&62.07&53.57&61.15\\
			BSR&0&0&0&7.76&14.29&8.46\\
			MRGP&0&0&0&0.86&17.86&2.69\\
			\hline
		\end{tabular}
\end{table}

\begin{table}[!htb]
	\caption{Comparison with noise level 0.01}\label{tab:comp_noise001}
	\centering
	\begin{tabular}{l|rrr|rrr} \hline
		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
		RILS-ROLS&\bf{36.29}&\bf{22.14}&\bf{34.77}&\bf{64.91}&\bf{46.43}&\bf{62.92}\\
		gplearn&13.21&8.93&12.75&14.22&7.14&13.46\\
		DSR&8.41&16.07&9.23&17.24&14.29&16.92\\
		EPLEX&8.77&0&7.83&14.22&3.57&13.07\\
		AFP&7.11&0.89&6.44&8.19&7.14&8.08\\
		AFP\_FE&6.12&3.57&5.85&5.6&0&5\\
		ITEA&0.11&0.89&0.19&1.72&10.71&2.69\\
		AIFeynman&0&0.79&0.09&0&0&0\\
		Operon&0.09&0&0.08&0&0&0\\
		GP-GOMEA&0&0&0&0&0&0\\
		SBP-GP&0&0&0&0&0&0\\
		BSR&0&0&0&0&0&0\\
		FEAT&0&0&0&0&14.29&1.54\\
		FFX&0&0&0&0&0&0\\
		MRGP&0&0&0&0&0&0\\
		\hline
	\end{tabular}
\end{table}

@@
